Salmon straying description

### 2017-04-26 manuscript/msv1.tex
MDPE fig for heterogeneous environs

Here we consider a local population $N_i$ and a remote population $N_j$, each with a trait value $x_i$ and $x_j$ that determines the recruitment rate, are assumed to be normally distributed with means $\mu_i$ and $\mu_j$ and a standard deviation $\sigma$, and are subject to selection across ecological timescales.
Each population in its respective site has an optimum trait value $\theta_i$ where the rate of recruitment is maximized if $x_i = \theta_i$.
If there is no straying between these populations (such that they are independent), then the trait value should evolve towards the optimum ($x_i \rightarrow \theta_i$) and the recruitment rate will become maximized.
If there is straying between populations at rate $m$, then the traits in each respective location will be pulled away from the optimum, and recruitment rates will be lower, i.e. have lower fitness.
As $m$ becomes large, the populations should act as a single population.

@@

% Constant m
%% Fold bifurcation @ intermediate values of m
%% PE > 1 for low values of m
%% Spike in PE at the fold bifurcation (spike in indvidual population SD)
%% Increased environmental heterogeneity leads to spikes in PE at lower stray rates
%% Effects of heritability vs. trait variation and stable states

>>>>

Here we consider a local population $N_i$ and a remote population $N_j$ with a trait value $x_i$ and $x_j$ that determines the recrutiment rate for the respective population.
We assume that there is an optimum trait value $\theta_i$ and $\theta_j$ associated with each site, where recruitment is maximized if $x = \theta$.

Each population in its respective site has an optimum trait value $\theta_i$ where the rate of recruitment is maximized if $x_i = \theta_i$.

determines the recruitment rate, are assumed to be normally distributed with means $\mu_i$ and $\mu_j$ and a standard deviation $\sigma$, and are subject to selection across ecological timescales.

If there is no straying between these populations (such that they are independent), then the trait value should evolve towards the optimum ($x_i \rightarrow \theta_i$) and the recruitment rate will become maximized.
If there is straying between populations at rate $m$, then the traits in each respective location will be pulled away from the optimum, and recruitment rates will be lower, i.e. have lower fitness.
As $m$ becomes large, the populations should act as a single population.

@@

%The effects of trait evolution :: trait heritability, trait variance, and habitat heterogeneity
%% When stray rates are moderate-low, greater heritability leads to higher steady-state populations with higher PE's.
%% Lower heritability gives way to alternative stable states at lower stray rates, which become increasingly divergent
%% With habitat heterogeneity?

% Constant m
%% Fold bifurcation @ intermediate values of m
%% This bifurcation creates a region of depressed total biomass & depressed PE at increased stray rates and lower trait variances

%% PE >> 1 for low values of m
%% Spike in PE at the fold bifurcation (spike in indvidual population SD)
%% Increased environmental heterogeneity leads to spikes in PE at lower stray rates
%% Effects of heritability vs. trait variation and stable states
